\renewcommand\bibname{References}
\begin{thebibliography}{9}

%\bibitem{}
%
%
%
\bibitem{}\begin{CJK}{UTF8}{ipxm}王叡鵬，原口誠： 構造類似性の列挙問題\end{CJK}, FIT 2017, Tokyo, Sep 2017

\bibitem{}\begin{CJK}{UTF8}{ipxm}全新受事件の最近５年間の推移『全裁判所』\end{CJK}, Courts in Japan, http://www.courts.go.jp/

\bibitem{}\begin{CJK}{UTF8}{ipxm}判例データーベース第一法規株式会社『D1-law.com』\end{CJK}, http://www.d1-low.com/.

\bibitem{}\begin{CJK}{UTF8}{ipxm}構文解析システム\end{CJK}KNP, http://nlp.ist.i.kyoto-u.ac.jp/index.php?KNP 


\bibitem{}Yukio Ohsawa,Nels E. Benson and Masahiko Yachida, KeyGraph: Automatic Indexing by Co-occurrence Graph based on Building Construction Metaphor,  pp.391-400, 1999.

\bibitem{}Etsuji Tomita, Akira Tanaka and Haruhisa Takahashi, The worst-case time complexity for generating all maximal cliques and computational experiments, Elsevier B.V., 2006.

\bibitem{}Takashi Nakagawa and Etsuji Tomita, An algorithm for generating all Maximal Bipartite Cliques Based on CLIQUES that Generates All Maximal Cliques, IPSJ SIG Technical Report, 2006.

\bibitem{}C. Bron, J. Kerbosch, Algorithm 457, finding all cliques of an undirected graph, Comm. ACM 16 (1973) 575–577.

\bibitem{}Swaminathan,K., Tau: A domain-independent approach to information extraction from natural language documents. DARPA workshop on document management, Palo Alto, 1993.

\bibitem{}Ryohei Sasano and Sadao Kurohashi.
A Discriminative Approach to Japanese Zero Anaphora Resolution with Large-scale Lexicalized Case Frames, In Proceedings of the 5th International Joint Conference on Natural Language Processing (IJCNLP2011), pp.758-766, 2011.
\bibitem{}G.D.Plotkin A Note on Inductive Generalization, Machin Intelligence Vol.5, 153--163, 1970
\bibitem{}\begin{CJK}{UTF8}{ipxm}喜多陵\end{CJK}, \begin{CJK}{UTF8}{ipxm}記述の構造類似性に基づく法的観点と判例のマッチング\end{CJK}, 修士論文, Hokkaido University, Graduate School of Information Science and Technology, 2014.

\bibitem{}Xiaolong Zhang, Towards a Detection of Descriptive Similarities among Multiple Precedents Based on Formal Concept Analysis, Master Thesis, Hokkaido University, Graduate School of Information Science and Technology, 2016.


\end{thebibliography}
