\section{Multi-document Summarization}
A multi-document summarization is an automated program designed to extract information from multiple texts of the same subject. The resulting summary report allows individual users such as professional information consumers to quickly become familiar with the information in a large number of document sets. In this way, the multi-document summary system is supplementing the next step to process the information overloaded news aggregator.\\
The information report of Multi-document summarization created is both concise and comprehensive. Putting different opinions together and summarizing, each topic is described from multiple perspectives in a single document. While the goal of a brief summary is to simplify information search and cut the time by pointing to the most relevant source documents, the comprehensive multi-document summary should itself contain the required information, hence limiting the need for accessing original files to cases when refinement is required. The automatic summary provides information that is extracted from multiple sources without any editorial touch or subjective intervention, making it completely unbiased.\\
Because the result of Multi-document summarization is one brief summary, it becomes a little different from our research. For a set of document, there exist a lot of descriptive patterns depend on the complexity of the document set. We can only extract some major ones from them, hence our research becomes a kind of data mining problem. We can also extract some similar point from some very different documents. That is very different with Multi-document summarization.\\ 